# Tables

(ref:tabletaxa) Species and groups of taxa used the analyses. Each species code, species common English name and scientific name appear in this Table. Whether a species is subjected to sex-dependent sampling, and whether size classes are assigned to a taxon, appear in the last two columns of the Table.

```{r tabletaxa, results="asis"}
csv.fn <- "species-list.csv"
my.specs.df <- read.csv(file=file.path("data", csv.fn))

my.specs.df$species.code <- as.character(my.specs.df$species.code)

csas_table(my.specs.df,
           caption = "(ref:tabletaxa)",
           format="latex"
)
```

\clearpage


(ref:tablemodels) Models considered.

```{r tablemodels, results="asis"}
knitr::opts_knit$set(latex.tilde = "\\hlopt{\\scriptsize{\\ensuremath{\\sim}}}")

csv.fn <- "models-considered.csv"
t.df <- read.csv(file.path("data", csv.fn))

# t.df$model.formula <- gsub("\\~", "\\\\$sim$", t.df$model.formula)

csas_table(t.df,
           caption = "(ref:tablemodels)",
           format="latex"
)
```

\clearpage

\begin{landscapepage}
\begin{scriptsize}

(ref:tablemodelsfits) Model fits.

```{r tablemodelsfits, results="asis"}
csv.fn <- "AIC-BIC-table.csv"
t.df <- read.csv(file.path("data", csv.fn))

values.vars <- names(t.df)[3:ncol(t.df)]
t.df[,values.vars] <- round(t.df[,values.vars],2)
t.df$species <- as.character(t.df$species)
  
csas_table(t.df,
           caption = "(ref:tablemodelsfits)",
           format="latex"
)
```

\end{scriptsize}
\end{landscapepage}

\clearpage



(ref:tablebestmodelsfits) Model fits.

```{r tablebestmodelsfits, results="asis"}
csv.fn <- "best-AIC-BIC-table.csv"
t.df <- read.csv(file.path("data", csv.fn))
names(t.df) <- gsub("_",".",names(t.df))
t.df$species <- as.character(t.df$species)
  
csas_table(t.df,
           caption = "(ref:tablebestmodelsfits)",
           format="latex"
)
```
